This is the title [Article v\versionnumber]

### 2022-03-31 manuscript/manuscript.tex
Update manuscript.tex
Discussion on the entropy portion

\section{Theory}
GIST is an implementation of Inhomogeneous Solvation Theory (IST) \cite{Lazaridis1998} that calculates the free energy of solvation $\dgsolv$ on a 3-dimensional grid.
It was first devised by Nguyen et al. \cite{Nguyen2012} and its implementation in \software{cpptraj} was thoroughly described in \cite{Ramsey2016}.
Here, we only provide a short overview of the theory behind GIST.
For more detailed information, we recommend one of the more recent publications on developments in GIST. \cite{Kraml2020}\cite{Chen2021}
\section{GIST study of streptavidin/biotin}

\subsection{Inhomegeneous Solvation Theory}

\subsection{Solvation Entropy}

\begin{equation}
    \Delta S_\textit{solv} = \Delta S_\textit{sw} + \Delta S_\textit{ww}
\end{equation}

@@

\subsection{Entropy Calculations in Cpptraj}
\subsubsection{Translational and Orientatonal Entropy}

\begin{equation}
    g_\textit{vox} \left( \textbf{r}, \mathbf{\omega} \right) \approx g_\textit{vox} \left( \textbf{r})g_\textit{vox}(\mathbf{\omega} \right)
\end{equation}

@@

\subsubsection{Sixth Order Entropy}
\begin{equation}
    S_\textit{k} \approx \frac{-R}{N_\textit{k}} \left( \sum _{i=1}^{N_k} ln g_{NN, \textit{i}} \left( \textbf{r}, \mathbf {\omega} \right) + \gamma \right)
\end{equation}

\subsection{Solvation Energy}
\subsubsection{PME implementation}

>>>>

\section{Theory}
GIST is an implementation of Inhomogeneous Solvation Theory (IST) \cite{Lazaridis1998} that discretizes  the free energy of solvation $\dgsolv$ on a three-dimensional grid. 
It was first devised by Nguyen et al. \cite{Nguyen2012} to overcome the limitation of IST which was commonly used for regions of high water occupancy and its implementation in \software{cpptraj} was thoroughly described in \cite{Ramsey2016}.
Here, we only provide a short overview of the theory behind GIST.
For more detailed information, we recommend one of the more recent publications on developments in GIST. \cite{Kraml2020}\cite{Chen2021}

\subsection{Solvation Entropy}
The solvation entropy of a system is totality of the contribution of the  solute-water entropy and the water-water entropy.

\begin{equation}
	\Delta S_\textit{solv} = \Delta S_\textit{sw} + \Delta S_\textit{ww}
\end{equation}
Here the solvation entropy is approximated from the contribution of solute-water interaction. 
\textbf{STILLNEEDS REVISON + ADD CITATIONS} The quantity $k_\textit{b}$represents the Boltzman constant, 
$\rho^\textit{o}$ is the bulk number density, $g_\textit{sw}\left(\textbf{r},\omega \right)$ is the solute-water 
pair correlation function in the solute's frame of reference, \textbf{r} is the coordinates of the oxygen atom of the water molecule,  
$\omega$ is the Euler angle, and the factor $\frac{1}{8\pi^2}$ is the normalization constant. In bulk and in regions where the orientational 
entropy is uniform, the quantity $g_\textit{sw}\left(\textbf{r},\omega \right)$ is unity which leads to the first-order solvation entropy of 
bulk to be zero. Also, this quantity reaches unity as the distance from the solute molecule increases which leads for the calculation of 
the solvation entropy to be an approximation of the integral around the solute atom.

@@

The solvation entropy is further broken down in terms of the contribution from translational and orientational terms.
\begin{equation}
	\Delta S_\textit{solv} = \Delta S_\textit{trans} + \Delta S_\textit{orient}
\end{equation}

\subsection{Entropy Calculations in Cpptraj}
In \software{cpptraj} the calculation of  solvation entropy is handled into two methods.

The first method assumes that the position ($r$) is independent of the orientation ($\omega$). This approximation allows for the 
splitting of the contributions of the translational and the orientational entropy. The nearest neighbor (NN) approach is used to 
evaluate each expression where $N_\textit{k}$ is the number of water molecules found in voxel k, $\gamma$ is the Euler's constant 
that accounts for the bias in naive entropy estimator, and $g_\textit{NN}$ is the nearest neighbor estimate. In the nearest neighbor
estimate, a voxel is considered to be a neighboring voxel when it shares any vertices of the voxel of interest. 
\begin{equation}
	g_\textit{vox} \left( \textbf{r}, \mathbf{\omega} \right) \approx g_\textit{vox} \left( \textbf{r})g_\textit{vox}(\mathbf{\omega} \right)
\end{equation}

@@

The second method directly calculates the solvation entropy by evaluating the six-dimensional integral (3 for position and 3 for orientation) 
using the nearest-neighbor approach. Unlike the first method, the nearest neighbor estimate for the sixth-order entropy considers all the water 
found within the same and neighboring voxels.  
\begin{equation}
	S_\textit{k} \approx \frac{-R}{N_\textit{k}} \left( \sum _{i=1}^{N_k} ln g_{NN, \textit{i}} \left( \textbf{r}, \mathbf {\omega} \right) + \gamma \right)
\end{equation}

\subsection{Solvation Energy}
\begin{equation}
	\Delta E_\textit{solv} = \Delta E_\textit{sw} + \Delta E_\textit{ww}
\end{equation}

\begin{equation}
	\Delta E_\textit{sw} = \rho^\textit{o} \int g_\textit{sw}\left(\textbf{r}\right) \Delta E_\textit{sw} \left(\textbf{r}\right) d\textbf{r}
\end{equation}

\begin{equation}
	\Delta E_\textit{ww} = \rho^\textit{o} \int g_\textit{sw}\left(\textbf{r}\right) \Delta E_\textit{ww} \left(\textbf{r}\right) d\textbf{r}
\end{equation}

\subsection{PME implementation}
